Preprocessing summary

### 2017-10-27 inst/examples/20151209-HelsinkiDH.Rmd
rOpenGov links to COMHIS links

This markdown document contains presentation material for [Digital History in Finland seminar (University of Helsinki, Dec 9, 2015)](http://blogs.helsinki.fi/mstolone/2015/09/21/call-for-papers-digital-history-in-finland-wednesday-9-12-2015/). The source code to reproduce the figures is in the [Rmarkdown document](https://github.com/rOpenGov/fennica/blob/master/inst/examples/20151209-HelsinkiDH.Rmd).

>>>>

This markdown document contains presentation material for [Digital History in Finland seminar (University of Helsinki, Dec 9, 2015)](http://blogs.helsinki.fi/mstolone/2015/09/21/call-for-papers-digital-history-in-finland-wednesday-9-12-2015/). The source code to reproduce the figures is in the [Rmarkdown document](https://github.com/COMHIS/fennica/blob/master/inst/examples/20151209-HelsinkiDH.Rmd).

### 2017-10-27 inst/examples/20170201-manuscript.Rmd
rOpenGov links to COMHIS links

The historical population sizes used in this analysis are shown in this [table](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/population_sizes_in_cities.csv).

>>>>

The historical population sizes used in this analysis are shown in this [table](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/population_sizes_in_cities.csv).

### 2017-10-27 inst/examples/summary.Rmd
ok
rOpenGov links to COMHIS links

[Self-published accepted](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/self_published_accepted.csv) (Check for formatting and synonymes)

[Self-published raw fields](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/self_published_rawfields.csv) (Check that the self-publication is a correct classification for these docs)

@@

[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)

[Discarded corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)

@@

[Complete geoplace listing](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)

>>>>

[Self-published accepted](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_accepted.csv) (Check for formatting and synonymes)

[Self-published raw fields](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_rawfields.csv) (Check that the self-publication is a correct classification for these docs)

@@

[Accepted corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)

[Discarded corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)

@@

[Complete geoplace listing](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)
